Satellite Alignments in Galaxy Pairs

### 2016-05-24 paper/ms.tex
seleccion de la muestra

We extract from the simulation spheres of $2$ \hMpc in radius around
the pair's center of mass. 
We use this information to exclude all the pairs that inc

in this
spherical volume a with a circular larger than $150$ km s$^{1}$. 
This further reduces the sample to $49$ pairs

Reduced sample based on non interacting halos. Further sub-selection
based on number of bright substructures.

Reduced Local Group sample based on kinematic characteristics.

@@

\begin{figure}
\centering
\includegraphics[width=\hsize]{v_circ_pairs.pdf}\\
\caption{Diference between the maximum circular velocity $V_{max}$ for the two
  halos in the pair as a function of $V_{max}$ for the massive halo in
  the pair.}
\label{fig:vcirc}
\end{figure}

>>>>

We extract from the simulation spheres of $2$ \hMpc in radius around
the pair's center of mass. 
We use this information to exclude all the pairs that have separations
smaller than the sum  of their virial radii, i.e. we exclude
interacting pairs. 
This reduces to $49$ the number of pairs in the sample.

We count the number of galaxies with $M_V<-9$ inside the virial
radius of each halo, including the central galaxy.
We only keep pairs where both halos have 5 bright galaxies at least. 
This reduces the sample to $24$ pairs. 
We call this sample the Full  Sample.

From the Full Sample we build a second sample based on the pairs' kinematics. 
Figure \ref{fig:samples} shows the comoving separation and relative
speed between the two halos in the pair.
The stars in the Figure represent the pairs with a separation in the
range $0.75\hMpc <R_{AB}< 1.50\hMpc$ and relative velocity in the
range $V_{AB}>100$ km s$^{-1}$, which are close to the Local Group
Observed values.
We call this sample the LG Sample.

The number of pairs in the Full Sample is consistent with previous
calculations. 
\cite{ForeroRomero2013} performed a study of the LG kinematics using a
cosmological N-body simulation as a benchmark. 
In their study, using criteria similar to ours to define the Full
Sample, they found 1923 pairs in a volume of $250^3$ $h^{-3}$
Mpc$^{3}$. 
With the same number density we expect to find $52$ pairs in the
volume of the Illustris simulation, which is very close to the actual
number of $49$ pairs.

In the same study they found 158 pairs with broad kinematic
caracteristics, similar to the definition of our LG sample. 
This represents a reduction of a factor of $12$ from their General
Sample. 
With those numbers in mind we would expect to keep at least $4$ pairs
in the Illustris volume. 
Given that our conditions are slightly more relaxed (we do not ask for
isolation criteria from massive halos) we end up with a larger sample
size, but still consistent with the fact that LG-like pairs are
scarce.

@@

%\begin{figure}
%\centering
%\includegraphics[width=\hsize]{v_circ_pairs.pdf}\\
%\caption{Diference between the maximum circular velocity $V_{max}$ for the two
%  halos in the pair as a function of $V_{max}$ for the massive halo in
%  the pair.}
%\label{fig:vcirc}
%\end{figure}
